---
title: "DAT 301 Lab 1"
output: pdf_document
date: "2024-03-23"
author: "Jason Kong"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
df = read.csv("Absenteeism_at_work.csv",sep=";",header=TRUE)
```

# 1. Plot the scatter plot of height vs. weight (so, weight on x-axis) including all the (non-missing) data.

```{r}
plot(df$Weight, df$Height, 
     xlab="Weight (kg)", 
     ylab="Height (cm)", 
     main="Height vs. Weight")
```

The graph suggests that most absentees have a body height between 165 and 175cm.

\newpage

# 2. Plot the histogram of hours of absences. Do not group by ID, just treat each absence as one observation.

```{r}
hist(df$Absenteeism.time.in.hours, 
     xlab="Hours", 
     main="Hours of Absence")
```
This graph suggests that most absentees have between 0-10 hours of absence.

\newpage

# 3. Plot the histogram of age of a person corresponding to each absence. Do not group by ID, just treat each absence as one observation.

```{r}
hist(df$Age, 
     xlab="Age", 
     main="Age of Absentees")
```

This graph indicates that a significant amount of absentees are between the age of 35 and 40.

\newpage

# 4. Plot the bar plot of hours by month. So, each month is represented by one bar, whose height is the total number of absent hours of that month. (Hint: you can use tapply().)

```{r}
hoursByMonth = tapply(X=df$Absenteeism.time.in.hours, INDEX=df$Month.of.absence, FUN=sum)
barplot(hoursByMonth, 
        xlab="Month", 
        ylab="Hours", 
        main="Hours by Month")
```
This graph suggests that the months of March and July see the most hours of absences.

\newpage

# 5. Plot the box plots of hours by social smoker variable. So, you will have two box plots in one figure. Use the legend, labels, title. Play with colors.

```{r}
boxplot(df$Absenteeism.time.in.hours ~ df$Social.smoker, 
        horizontal=TRUE, 
        col=c("palegreen","sienna"), 
        xlab="Hours", 
        ylab="Smoker?", 
        main="Hours by Smokers vs. Non-smokers")
legend("topright", legend=c("Smoker","Non-smoker"), fill=c("sienna","palegreen"))
```

This graph indicates that non-smokers have a lower median hours of absence.

\newpage

# 6. Plot the box plots of hours by social drinker variable. So, you will have two box plots in one figure. Use the legend, labels, title. Play with colors.

```{r}
boxplot(df$Absenteeism.time.in.hours ~ df$Social.drinker, 
        horizontal=TRUE, col=c("cornflowerblue","coral"), 
        xlab="Hours", 
        ylab="Drinker?", 
        main="Hours by Drinkers vs. Non-drinkers")
legend("topright", legend=c("Drinker","Non-drinker"), fill=c("coral","cornflowerblue"))
```

This graph indicates a higher median hours of absence among drinkers when compared to non-drinkers.